Verifying Demonstrations

### 2019-02-27 paper/protocol.tex
turns protocol overview figure into text

The core of the \CROCUS protocol consists of generating participation
proofs (joining a protest, participating in witnessing, submitting
proof shares to a ledger, all in \cref{ProtocolDuring}) with an overview in \cref{fig:ProtocolOverview}, and then counting and
verification of that count (in \cref{ProtocolVerification}).

@@

%The join, participation and submission phases are as follows.
% illustrated in \cref{fig:ProtocolOverview}.
The goal of \CROCUS is to generate and collect privacy-preserving
participation proofs that can be counted and verified. These proofs
consist of proof shares that are constructed as depicted in
\cref{fig:ProofFig}. The protocol phases are given in
\cref{fig:ProtocolOverview} and described below.

@@

\begin{figure}
 \centering
 % \small
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\wid})],\quad \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\pid})],\quad \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of \CROCUS participation.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
   public ledger for permanent storage \(S\). Note that \pid  always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure}
%\normalsize

>>>>

The core of the \CROCUS protocol consists of generating participation
proofs (joining a protest, participating in witnessing, submitting
proof shares to a ledger, all in \cref{ProtocolDuring}), and then counting and
verification of that count (in \cref{ProtocolVerification}).

@@

%The join, participation and submission phases are as follows.
% illustrated in \cref{fig:ProtocolOverview}.
The goal of \CROCUS is to generate and collect privacy-preserving
participation proofs that can be counted and verified. These proofs
consist of proof shares that are constructed as depicted in
\cref{fig:ProofFig}.

@@

% \begin{figure}
%  \centering
%  % \small
%   \begin{minipage}{\linewidth}
%     \begin{align*}
%       O\to \text{all}\colon & \text{manifesto} \\
%       P\colon & t_s\gets \TSget \\
%         & \cid\gets \Hash[\text{manifesto}], \\
%         & \pid\gets \ACprf[_{\sk_P}][\cid] \\
%       W\colon & t_s'\gets \TSget
%       \\[-1em]
%       \noalign{\hfill Join}
%       \midrule
%       \noalign{\hfill Participation}
%       \\[-3em]
%       P\to W\colon & \pid \\
%       P\leftrightarrow W\colon &
%         \PPK\mleft\{ (\sk_P) : \mright. \\
%         & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
%         & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
%         \\
%       W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
%       W\to P\colon & (\wid, t_s', l)
%       \\[-1em]
%       \noalign{\hfill Participation}
%       \midrule
%       \noalign{\hfill Submission}
%       \\[-2em]
%       P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
%       W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
%       W\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
%       \pi_{\wid})],\quad \text{where} \\
%         & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
%         & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
%         & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
%         \\
%         & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
%       P\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
%       \pi_{\pid})],\quad \text{where}\\
%         & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
%         & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
%         & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
%         \\
%         & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
%     \end{align*}
%   \end{minipage}
%   \caption{%
%     An overview of \CROCUS participation.\@
%     The organizer \(O\) broadcasts the manifesto.
%     The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
%     Finally, both \(P\) and \(W\) submit the proof shares to a
%    public ledger for permanent storage \(S\). Note that \pid  always refers to the
%     protester whose presence is being witnessed.
%   }%
%   \label{fig:ProtocolOverview}
% \end{figure}
% %\normalsize

We now give an overview of \CROCUS participation.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
   public ledger for permanent storage \(S\). Note that \pid  always refers to the
    protester whose presence is being witnessed. More formally:

 % \small
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\wid})],\quad \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\pid})],\quad \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
 %\normalsize
